\documentclass[letterpaper,MMMyyyy,nonstopmode]{style}
\usepackage{comment}
\usepackage[inline]{enumitem}
\usepackage{multicol}
\newcommand{\CVAuthor}{Kevin Zou}
\newcommand{\CVTitle}{Kevin Zou's Resume}
\newcommand{\CVNote}{Last Update \today}
\newcommand{\CVWebpage}{}

\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfkeywords={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
{6918 Rosemont Drive, McLean, Virginia 22101, USA}
\par
\href{mailto:kevinzou2150@gmail.com}{kevinzou2150@gmail.com}
\,\SubBulletSymbol\,+1\,(703)\,362-6362
\par
\CVNote
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.umich.edu/}
{\textbf{University of Michigan}},
Ann Arbor, VA, USA
\hfill
\DatestampYMD{2018}{9}{} -- Present
%\DatestampYMD{}{}{}
\Gap
\BulletItem
Undergraduate Student
\hfill
Expected Graduation: May 2022
\BulletItem
Computer Science Major
\Gap

\Entry
\href{https://tjhsst.fcps.edu/}
{\textbf{Thomas Jefferson High School for Science and Technology (TJHSST)}},
Alexandria, VA, USA

\Gap
\BulletItem
Graduated with Advanced Studies Diploma
\hfill
\DatestampYMD{2014}{9}{} --
\DatestampYMD{2018}{6}{9}
\BulletItem
Cumulative GPA of 4.224


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\href{http://cs.gmu.edu/~ashehu/}
{\textbf{Computational Biology Research Mentorship}},
George Mason University
\hfill
\DatestampYMD{2017}{06}{22} -- 
\DatestampYMD{2018}{06}{04}

\Gap
\BulletItem
Project:
Memetic Evolutionary Algorithms for De-novo Protein Structure Prediction
\BulletItem
Mentor:
Dr. Amarda Shehu, Computer Science Department
\BulletItem
Topics:
Computational biology, genetic algorithms, de novo protein structure prediction, stochastic optimization

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%
% START COMMENT
\begin{comment}
\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Conferences}
{Conferences}
{PDF:Conferences}

\begingroup
\renewcommand{\MaxNumberedItem}{[8888]}

\Gap
\NumberedItem{[1]}
{\underline{Kevin Zou} and Amarda Shehu,
``Memetic Evolutionary Algorithms for De-novo Protein Structure Prediction,''
\textit{ACM Bioinformatics and Computational Biology Conference, 2018}. In Preparation.}

\endgroup
\end{comment}
% END COMMENT

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\Gap
\BulletItem
HackGT CTF 3rd Place
\hfill
\DatestampYMD{2018}{10}{}
\begin{Detail}
\Item
Placed 3rd out of 71 teams in the HackGT Hackathon's CTF competition for computer security.
\end{Detail}


\Gap
\BulletItem
HackUVA Hackathon Winner, Domain.com Sponsored Award
\hfill
\DatestampYMD{2018}{03}{25}
\begin{Detail}
\Item
Won the Domain.com sponsored award for an atomated stock and option trading web app.
\end{Detail}

\Gap
\BulletItem
AP Scholar with Honors,
CollegeBoard
\hfill
\DatestampY{2018}
\begin{Detail}
\Item
Obtained the highest score, 5, on 4 AP exams, with an average of 4.6 on all AP exams taken\end{Detail}

\Gap
\BulletItem
National Merit Scholarship Semifinalist, NMSC
\hfill
\DatestampYMD{2017}{09}{11}
\begin{Detail}
\Item
Achieved an index score of 225 on the 2016 PSAT, which qualified me as a semifinalist for the NMSC.
\end{Detail}

\BulletItem
PilotDC Hackathon "Most Innovative" Award
\hfill
\DatestampYM{2015}{08}
\begin{Detail}
\Item
Awarded for an Image Recognition application that controlled a computer's mouse through eye movements.
\end{Detail}

%%%%%%%%%%%%%%
%% PROJECTS %%
%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}

\Entry
{\textbf{UM::Autonomy, Autonomous Boat Team}}, University of Michigan
\hfill
\DatestampY{2018} -- Present
\Gap
Programmed drivers for sensors and embedded systems on an autonomous boat, in addition to processing the data from the sensors for use in other systems within the boat.
\Gap
\Entry
{\textbf{Image Processing Intern}}, Kashmir World Foundation
\hfill
\DatestampY{2016} -- {2018}
\Gap
Programmed drones to autonomously track sea turtles for animal conservation. I organized image data sets, trained neural networks to recognize and classify turtle tracks, and worked on optimizing the image recognition to run locally on a custom-built drone.
\Gap
\Entry
{\textbf{TJREVERB Cubesat Project}}, TJHSST
\hfill
\DatestampY{2016} -- \DatestampY{2018}
\Gap
Student-run project to send a satellite into orbit. I contributed code for our outreach website and the satellite's radio communications. Greenlit by NASA for a 2019 launch.
\Gap
\Entry
{\textbf{Open-Source Video Game-related Development}}
\hfill
\DatestampY{2015} -- Present
\Gap

Writing short videogame scripts and reverse-engineering tools to modify and emulate games.

Developed a custom command-line client/emulator for an MMO game, allowing users to chat and carry out simple tasks (trade, view friends, etc) without the need to open the full game client. %Runs on all major operating systems and also Android phones.

In Development: a spreadsheet based web database for the mobile game Doll's Frontline, providing stats and info on various characters within the game.

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}
English: Native language

Chinese: Basic (speaking)

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
{\textbf{Programming}}
\Gap
Proficiencies: Debugging, Profiling
\Gap
Advanced:
C++ \SubBulletSymbol \space 
Javascript \SubBulletSymbol \space 
Node.js \SubBulletSymbol \space
Python
\Gap
Intermediate:
OpenCV \SubBulletSymbol \space
Java
%\Gap

%\Entry
%{\textbf{Office}}
%\Gap
%Advanced:
%Microsoft Word / Excel \SubBulletSymbol \space
%LaTeX Typesetting

\end{Body}

\end{document}
